---
title: "Assignment 1"
date: "1/31/2022"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

# Background

You're approached by a faculty member in the NYU A3SR program who would like you to help them develop a simple visualization tool to help them see the distribution of their students grades. The faculty member teaches 2 class so the application will need to be able to switch between 2 different datasets. 

Some of the assignments are on a continuous scale, while others are on a discrete scale. The faculty member would prefer to see grades as a histogram for continuous variables and a barchart for discrete variables. For the continuous assignments, the faculty member likes the idea of having the option to group the histogram by any of the discrete variables (i.e. a grouped histogram). 

Due to privacy laws the faculty member can not share the grades with you but asks you to code up a prototype using the `penguins` and `mtcars` datasets. 

Can you build the prototype? 

# Data
Assignment 1 will involve using both the `penguins` and `mtcars` datasets. `mtcars` is native to R and penguins is in the `palmerpenguins` package. The code chunk below is an example of how to load both datasets

```{r, eval=FALSE}
require(palmerpenguins)
penguins
mtcars
```

# Part 1 
## Simple Data Summary
1. Create a Shiny app named hw1_part1
2. In hw1_part1 you will create a data visualization app with the following criteria: 
* The user can switch between either the `penguins` dataset or the `mtcars` dataset
* The app allows the user to select a variable and see a histogram if the variable is continuous and a bar chart for discete  variables.
* When the user has selected a continuous variable, give them the option to color the histogram by a discrete variable. 

An example of this type of a plot is shown below: 

```{r}
library(ggplot2)
ggplot(data = diamonds, aes(price, fill = color)) + 
  geom_histogram(bins = 25, alpha = .7, position = 'identity')

```

  * Any variable that is a string or has less than 5 unique values is a discrete variable
  
# Part 2
## Changing the UI
1. Create a Shiny app named hw1_part2
2. Recreate your app from part1 but with a some simple UI modifications

Modifying the UI could include any of the following: 

* Changing the inputs used to select data, variables or plots (radio buttons instead of a drop down etc.)
* Adding new inputs such as the option to change bins
* Reorganizing the page layout (grid arrangement, tabs etc.)

# Grading 
**Submit to GitHub by 10PM Sunday February 6**

10 point scale discussed in class: 
4 points for attempting all sections 
3 points for submitting an app that compiles and runs
3 points for style

* commented code 
* well designed UI
* good use of R/R Shiny functions

